Biogears in Anesthesia Screen Based Simulation

### 2016-02-26 paper_working_on/paper.tex
restructure the tex and add cae jpg

\title{Biogears in Anesthesia Screen Based Simulation}

@@

\begin{abstract}
The delivery of good medical care concerns patients as well as medical professionals. In terms of medical training, mannequins used to be orthodox way to train and demonstrate medical skills for students. Nowadays, schools and institutions are adopting more and more high-tech involved methodologies such as Simulation-Based medical education, Virtual Reality in order to provide students with immersive and realistic experience of medical training. In Simulation-Based medical education particularly, whether the models of physiology incidents or responses are accurate or not will directly affect the credibility of the simulation. In this paper, we will give insights into the physiology simulation and compare the current physiology engine Biogears. We will evaluation its function by comparing with simulation provided by CAE Muse system. In the end, we will conclude on the performance of Biogears on key points such as authenticity, stability as well as commenting on its limitations.
\end{abstract}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{bleeding_out_HeartRate_vs_Time.jpg}}
     \caption{heart rate changes}
     \label{fig:patient bleeding}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{bleeding_out_RespirationRate_vs_Time.jpg}}
     \caption{respiratory rate changes}
     \label{fig:patient bleeding}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{30_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{120_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Succinylcholine_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Rocuronium_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Rocuronium_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 50 mg Rocuronium}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Rocuronium_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Rocuronium_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 50 mg Rocuronium}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Propofol_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 200 mg Propofol}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Propofol_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 200 mg Propofol}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Propofol_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 200 mg Propofol}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{Propofol_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 200 mg Propofol}
   \end{minipage}
\end{figure}

>>>>

\graphicspath{{cae_simulation_result/}}
\title{Biogears in Anesthesia Screen Based Simulation}

@@

\begin{abstract}
The delivery of good medical care concerns patients as well as medical professionals. In terms of medical training, mannequins used to be orthodox way to train and demonstrate medical skills for students. Nowadays, schools and institutions are adopting more and more high-tech involved methodologies such as Simulation-Based medical education, Virtual Reality in order to provide students with immersive and realistic experience of medical training. In Simulation-Based medical education particularly, whether the models of physiology incidents or responses are accurate or not will directly affect the credibility of the simulation. In this paper, we will give insights into the physiology simulation and compare the current physiology engine Biogears and CAE Muse software. We will evaluation Biogears function by comparing with simulation provided by CAE Muse system. In the end, we will conclude on the performance of Biogears on key points such as authenticity, stability as well as commenting on its limitations.
\end{abstract}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_HeartRate_vs_Time.jpg}}
     \caption{heart rate changes}
     \label{fig:patient bleeding}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/bleeding_out_RespirationRate_vs_Time.jpg}}
     \caption{respiratory rate changes}
     \label{fig:patient bleeding}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/30_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/120_OxygenSaturation_vs_Time.jpg}}
     \caption{oxygen saturation changes}
     \label{fig:patient stoping breathing}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 5 mg Succinylcholine}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Succinylcholine_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 5 mg Succinylcholine}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 50 mg Rocuronium}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 50 mg Rocuronium}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Rocuronium_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 50 mg Rocuronium}
   \end{minipage}
\end{figure}

@@

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_HeartRate_vs_Time.jpg}}
     \caption{Heart Rate changes}
     \label{fig:given 200 mg Propofol}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_OxygenSaturation_vs_Time.jpg}}
     \caption{Oxygen Saturation changes}
     \label{fig:given 200 mg Propofol}
   \end{minipage}
\end{figure}

\begin{figure}[!htb]\centering
   \begin{minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_ArterialPressure_vs_Time.jpg}}
     \caption{Blood Pressure changes}
     \label{fig:given 200 mg Propofol}

   \end{minipage}
   \begin {minipage}{0.49\textwidth}
     \frame{\includegraphics[width=5cm]{biogears_simulation_result/Propofol_RespirationRate_vs_Time.jpg}}
     \caption{Respiration Rate changes}
     \label{fig:given 200 mg Propofol}
   \end{minipage}
\end{figure}

\begin{figure}[p]
    \includegraphics[width=1\textwidth]{cae_propofol_200mg.png}
    \caption{Propofol vital signs}
    \label{fig:awesome_image}
\end{figure}
